\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template
		
		\bibitem{1}
		Otsu N.  
		\newblock {\em A threshold selection method from gray-level histograms[J].} 
		\newblock Automatica, 1975, 11(285-296): 23-27.
		
		\bibitem{2}
		Kittler J, Illingworth J. 
		\newblock {\em On threshold selection using clustering criteria[J].} 
		\newblock IEEE transactions on systems, man, and cybernetics, 1985 (5): 652-655.
		
		\bibitem{3}
		Sahoo P K, Soltani S, Wong A K C. 
		\newblock {\em A survey of thresholding techniques[J].} 
		\newblock Computer vision, graphics, and image processing, 1988, 41(2): 233-260.
		
		\bibitem{4}
		Chen D, Zhang F, He G. 
		\newblock {\em An Improved Binarization Algorithm for Document Image [J][J].} 
		\newblock Computer Engineering, 2003, 13: 032.
		
		\bibitem{5}
		Bernsen J.
		\newblock {\em Dynamic thresholding of grey-level images[C]} 
		\newblock International conference on pattern recognition. 1986, 2: 1251-1255.
		
		\bibitem{6}
		Hsia S C, Chen M H, Chen Y M. 
		\newblock {\em A cost-effective line-based light-balancing technique using adaptive processing[J].} 
		\newblock IEEE transactions on image processing, 2006, 15(9): 2719-2729.
		
		\bibitem{7}
		Gonzalez R C, Woods R E. 
		\newblock {\em Digital image processing[J].} 
		\newblock  2002.
		
		\bibitem{8}
		Ohbuchi E, Hanaizumi H, Hock L A. 
		\newblock {\em Barcode readers using the camera device in mobile phones[C]} 
		\newblock Cyberworlds, 2004 International Conference on. IEEE, 2004: 260-265.
		
		\bibitem{9}
		Sun A, Sun Y, Liu C.
		\newblock {\em The QR-code reorganization in illegible snapshots taken by mobile phones[C]} 
		\newblock Computational Science and its Applications, 2007. ICCSA 2007. International Conference on. IEEE, 2007: 532-538.
		
		\bibitem{10}
		Hu H, Xu W, Huang Q.
		\newblock {\em A 2D barcode extraction method based on texture direction analysis[C]} 
		\newblock Image and Graphics, 2009. ICIG'09. Fifth International Conference on. IEEE, 2009: 759-762.
		
		\bibitem{11}
		刘宁钟, 杨静宇. 
		\newblock {\em 基于波形分析的二维条码识别[J].} 
		\newblock 计算机研究与发展, 2004, 41(3): 463-469.
		
		\bibitem{12}
		Leong L K, Yue W.
		\newblock {\em Extraction of 2d barcode using keypoint selection and line detection[C]}
		\newblock Pacific-Rim Conference on Multimedia. Springer Berlin Heidelberg, 2009: 826-835.
		
		\bibitem{13}
		
		\newblock {\em } 
		\newblock
\end{thebibliography}